Named Entity Recognition on HTML as a web data extraction subtask

### 2018-09-21 tex/article.tex
Modifications to paper.

Web information extraction is the task of automatically extracting structured information
from unstructured or semi-structured web documents. The input usually consists of
web documents containing a number of predetermined entities organized in a similar 
manner and the information extraction task consists of identifying these entities
and organizing them according to a template. In this context, named entity recognition
(NER) is a subtask that aims to detect named entities in the text and classify them into 
predetermined categories such as person names, locations or organizations.

Once we are able
to reliably detect relevant entities, we may employ an information extraction 
algorithm to extract structured data. In this paper, we investigate different NER 
approaches from the perspective of web information extraction.

HTML documents most often lie in between the structured / unstructured data paradigm, 
which means that authors take quite a casual approach regarding formal structure. 
However, DOM hierarchy, element disposition, class names, and other features related to 
the document structure and indirectly associated with the data itself can be valuable 
information in the task of identifying entities and determining relationships. Yet we 
cannot expect these features to be completely constrained by an underlying pattern. 
Organization patterns tend to follow some guidelines but are in no way subject to 
strict rules. That is why classical information extraction systems such as automatic
wrapper generators usually do not translate well across different websites. Contrastingly, 
statistical based approaches can be much more flexible.

NER systems are frequently trained and tested on news corpora such as the 
dataset introduced at the Language-Independent Named Entity Recognition Shared Task
at CONLL-2003 \cite{Sang2003}. State-of-the-art approaches have recently achieved 
F1-scores of 90.10 \cite{Huang2015}, 90.94 \cite{Lample2016}, and 91.21 \cite{Ma2016} 
in this task using different combinations of bidirectional LSTM layers, word and 
character representations.

Even if focusing on web documents, records also may
contain pure text that needs appropriate IE algorithms to extract the inherent data. Most WDE algorithms certainly can exploit the semi-structured nature of web documents, but can surely not restrict ourselves to that, because deeper processing is necessary. When looking through the algorithms and searching for the Swiss army knife, most algorithms can be ruled out for some incapability restricting the algorithms strongly. B.

NER on HTML poses a different type of challenge, because web pages are often
very different from the plain text found in news corpora. Named entities may be present 
inside tables, lists, graphs or other types of visual elements that provide
little to no textual information that could give hints about the semantic category of 
a word. Systems trained on news or similar corpora do not translate well to the web
NER task without retraining, since in this task we cannot profit
as much from contextual hints or transfer learning approaches such as word embeddings.
Besides, deep learning approaches can require a lot of data to reach peak performance.

To test different NER approaches from the perspective of web information extraction,
we will explore the task of person names extraction from university faculty websites.
Researcher affiliation is often missing from many entries in public databases such as DBLP  
\footnote{
  http://dblp.uni-trier.de/
} and the display of information varies significantly between different university 
websites, so this task can provide a good measure of the expected performance and
data need for other web information extraction tasks. Also, with the lack of a large amount
of training data, we show that feature engineering and resources such as a gazetteer 
may be invaluable.

@@

Most data extraction systems focus on extracting information from single websites
and thus are unsuited for cross website extraction tasks. Even unsupervised
approaches that are domain independent, such as RoadRunner \cite{Crescenzi2001} 
and EXALG \cite{Arasu2003} only work well for extracting data from pages generated 
from the same underlying template. A statistical approach to unsupervised domain 
independent web data extraction was described by Zhu et al \cite{Zhu2005}. The 2D CRF 
model takes a web page segmented into data blocks and employs a two dimensional conditional 
random field model to perform attribute labelling. The model was further improved in 
\cite{Zhu2006} to model record segmentation and attribute labeling as a joint task.
Some of the limitations of early unsupervised methods 
were also tackled by ObjectRunner (\cite{Abdessalem2010}) and AMBER (\cite{Furche2012}). 
These methods work by annotating webpages automatically with regular expressions, gazetteers and 
knowledge bases. They can rectify low quality annotations and even improve the annotators
by exploring regular structures in the DOM during the record segmentation phase.

In summary, web data extraction methods have undoubtedly improved extraordinarily, but
as pointed by Schulz et al. \cite{Schulz2016}, it is difficult to compare the results 
achieved by competing tools, and many seem to rely excessively on certain heuristics.
In that regard, the impressive advancements in NLP may provide for more robust and
flexible extraction tools.

@@

Most web data extraction systems rely on hand crafted rules or gazetteers to perform
attribute annotation. Machine learning approaches to NER can improve annotations of 
more complex entities and even manage entity detection without resorting to a gazetteer.
We explored multiple approaches to the Named Entity Recognition problem in the context 
of a web information extraction task. We first introduce two traditional approaches, 
namely: Hidden Markov Models and Linear Chain Conditional Random Fields. And further
we explore the neural architectures.

@@

\begin{itemize}
\item Train the HMM in a given training set without the HTML features.
\item Compute labels for the new websites with the trained HMM.
\item Use these computed labels as a proxy for the actual labels in the 
new websites and estimate HTML feature frequencies only in the new websites.
\item Recompute the labels using the HTML features.
\end{itemize}

@@

Recurrent neural networks (RNN) have been succesfully employed on numerous NLP tasks such as
language modelling, POS tagging, speech recognition and NER. Different from feedforward neural networks, 
RNNs can retain information in their internal state, making them more suitable for processing sequences, 
and consequently for solving text related tasks. In NER, the network outputs one label for each input 
vector as Figure YYY.

<INSERT FIGURE YYY>

@@

\begin{flalign*}
\Gamma_i^{<t>} &= \sigma(W_i[x^{<t>},h^{<t-1>}] + b_i) &\\
\Gamma_f^{<t>} &= \sigma(W_f[x^{<t>},h^{<t-1>}] + b_f) &\\ 
c^{<t>}        &= \Gamma_f^{<t>} \circ c^{<t-1>} + \Gamma_i^{<t>} tanh(W_{c,x} x^{t} + W_{c,a} a^{t-1} + b_c) &\\
\Gamma_o^{<t>} &= \sigma(W_o[x^{<t>},h^{<t-1>}] + b_o) &\\
h^{<t>}        &= \Gamma_o^{<t>} \circ tanh(c^{t}) &
\end{flalign*}

where $ \sigma $ is the logistic sigmoid function. $ \Gamma_i $, $ \Gamma_f $, and $ \Gamma_o $ are the input,
forget and output gates, respectively. And $ W $ with a subscript is the weight 
matrix corresponding to that gate. Variable $ c^{<t>} $ is the cell 
state and $ h^{<t>} $ is the hidden state, with the vector $ [x^{<t>},h^{<t-1>}] $ 
being formed by concatenating the current input vector $ x^{<t>} $ and the hidden vector 
from the previous timestep $ h^{<t-1>} $. A visual description of our LSTM cell is 
provided in figure XXX.
This implementation differs from the LSTM cell described in Huang et al. \cite{Huang2015}
in that the input gate $ \Gamma_i $ and the forget gate $ \Gamma_f $
do not take input from the previous cell state $ c^{<t-1>} $ and the output gate does
not take input from the current cell state $ c^{<t>} $. The cell state and the control
gates are what makes the LSTM cell better at modelling long term dependencies in comparison
to a regular RNN.

XXX Insert figure explaining equations XXX

@@

\subsubsection{LSTM-CRF}

Huang et al. \cite{Huang2015} proposed a bidirectional LSTM with a CRF layer (LSTM-CRF) on the output to tackle
the sequence tagging problem. The CRF layer jointly decodes labels for the whole sentence instead
of predicting each label individually. This architecture achieved an F1 score of 90.10 in the 
ConL2003 dataset, in contrast to 85.17 for a bidirectional LSTM without the CRF layer. 
In our experiments, the LSTM-CRF architecture used a bidirectional LSTM with 100 
hidden states, no peepholes and an input and output dropout layers with a dropout
rate of 0.5. The dropout layers have proven to be very important to prevent overfitting 
and allow better generalization.

\subsubsection{LSTM-CRF + CNN character representations}

Ma and Hovy \cite{Ma2016} proposed adding a convolutional neural networks (CNN) layer 
on top of a bidirectional LSTM-CRF to encode character-level information. Those character
representations are combined with word level representations and then fed to the
Bidirectional LSTM. This architecture possesses the capacity to learn morphological
token features that are extremely useful on the NER task, since similar named entities 
often present morphological similarities. This improvement obtained an F1 score of 
91.21 at the ConLL2003 dataset. In our experiments, the LSTM-CRF architecture with
CNN character representations used a one dimensional convolutional neural network with 30 
filters and a window size of three characters on top of the LSTM-CRF architecture,
the character embeddings fed to the CNN had 30 dimensions that were randomly initialized.

@@

Lample et al \cite{Lample2016} suggested using an a bidirectional LSTM to model character-level 
representations on a bidirectional LSTM-CRF. Combining both the forward and backward 
LSTM representations to form the character representation. This character
representation is also combined with a word representation. The forward LSTM is expected to be a better
representation of the suffix of a token, and the backward LSTM is expected to be a
better representation of the prefix of a token. This differentiates the architecture
from the CNN based approach, because CNN filters discover positional invariant
features, while LSTMs can better represent suffixes and prefixes. In our experiments, 
the LSTM-CRF architecture with LSTM character embeddings was implemented by a bidirectional LSTM
with 25 hidden states, producing character representations of size 50. The character embeddings
also had 30 dimensions that were randomly initialized.

@@

The neural models were trained with Stochastic Gradient Descent over 50 epochs using a learning 
rate of 0.01 and momentum of 0.9. We used early stopping \cite{Caruana2000} to select the best 
parameters,  considering the F1 measure in the validation set. All neural models used 
GloVe 100-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training,
they have a vocabulary size of 400.000 words.
In the case of NER on HTML, word embeddings work as a rather satisfactory gazetteer. Named entities 
of a same type have similar embeddings, so with good word embeddings we can achieve exceptional 
performance with little training data and without a gazetteer. Figure XXX illustrates the differences
between the three neural models mentioned previously.

XXX Insert picture here explaining the models Figure 1 XXX

@@

We constructed a novel dataset to evaluate the performance of multiple NER models
at the web information extraction task. The task consists of finding researcher
names in faculty listings from multiple web pages. This would be the 
first step in linking researcher profiles from university websites to their entries
in public databases such as DBLP \footnote{http://dblp.uni-trier.de/}. Unlike many
information extraction datasets, each web page in the dataset comes from a different 
university, and therefore has a different format, what makes many information
extraction approaches impractical. The idea is to explore systems that are general 
enough to allow efficient name extraction from many different sources without requiring
any supervision between different websites.

This task would be similar to the task of labeling authors in comments
from many different sources or labeling authors in articles collected from many
publishing platforms. Another similar task would be NER on tweets. Because of the character
limitation present on tweets, we end up with constraints comparable to the ones 
found in the NER on HTML task, so we expect similar systems to have comparable performances
on both of these tasks.

We collected 145 computer science faculty pages from 42 different countries in 
multiple languages, although the English version was prefered when it was available. 
We gathered faculty web pages randomly in proportion to 
the number of universities in each country\footnote{A detailed list of universities can 
be found in https://univ.cc/world.php}. Each HTML page was preprocessed and converted
to the CONLL 2003 data format. That is, one word per line with empty lines representing
sentence boundaries. Sentence boundaries were determined by line break HTML tags
(div, p, table, li, br, etc.) in contrast to inline tags (span, em, a, td, etc.). Sentences
that were more than 50 tokens were also split according to punctuation.

A proper HTML segmenter poses many challenges by itself as discussed for example in \cite{Cai2003}.
However, we wanted to evaluate models without relying on any sophisticated data record
segmentation system. In many cases, entity annotation may precede the segmentation
phase in web data extraction methods, so annotators have to be able to work with
raw HTML data. Because of the type of documents present in the dataset, many sentences 
contained only one or two tokens, while other documents contained long texts.
Finally, all tokens were tagged using the IOB scheme put forward by
Ramshaw and Marcus \cite{Ramshaw1995} with a modification. O stands for Outside, 
B-PER is the beginning of a person name, I-PER inside a person name and PUNCT is any 
punctuation sign other than ".". Many name representations contain punctuation signs 
and the PUNCT label helps predicting label transitions properly, especially when using 
simpler algorithms like HMMs. A name for example never ends with a punctuation sign,
but it may be split by a punctuation sign.

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l| }
      \hline
      Feature & Description \\
      \hline
      1  & Unaccented lowercase token \\
      2  & Exact gazetteer match \\
      3  & Partial gazetteer match \\
      4  & Log name gazetteer count\\
      5  & Log word gazetteer count\\
      6  & Email \\
      7  & Number \\
      8  & Honorific \\
      9  & URL \\
      10 & Is capitalized \\
      11 & HTML tag + parent \\
      12 & CSS class \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Features present in the bla dataset}
  \label{tab:features}
\end{table}

The unaccented lowercase token was used as the key for the Glove-100 embedding lookup.
A gazetteer was constructed from a researcher list extracted from DBLP with 1.595.771
names. Feature 2 represents an exact match of a sequence of tokens to any of the 1.595.771 
names, and feature 3 represents a partial match. Feature 4 is the rounded logarithm of 
the frequency of a token in the gazetteer, and feature 5 is the rounded logarithm of the frequency
of a token in a word corpus obtained through a random crawl in university websites.
Features 6 to 9 represent a simple regular expression match to an email, number, 
honorific or URL, respectively. Feature 10 represents if a word is capitalized.

Feature 11 represents the HTML enclosing tag and its parent concatenated. Feature 12
represents all CSS classes concatenated. These features are not very useful in a general
sense, because every HTML document has a different format, so only because a named entity
occurs inside a given HTML tag in a document we cannot say it is more likely to be the case 
in other documents. However, these features can be trained with the self-training strategy 
for HMMs described in section \ref{sssec:self_training}. For all other models these features 
were ignored.

@@

We conducted two experiments to evaluate the best models for named entity recognition
on HTML in the context of web data extraction. In the first experiment, we used the
whole training set (90 documents). In the second experiment, the training set was split 
into five non overlapping sets with only 18 documents and the validation set was reduced 
to 5 documents, but the test set was kept unchanged. The goal of this second experiment 
was to evaluate models when training data is scarce, since labelling data can be a very 
time consuming task.

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l|l|l|l|l|l| }
      \hline
      \multirow{2}{*}{Model} & \multicolumn{3}{c|}{Validation} & \multicolumn{3}{c|}{Test} \\
                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1}
                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1} \\
      \hline
      hmm-1           & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      hmm-2           & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      hmm-3           & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      crf             & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      lstm-crf        & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      lstm-crf-cnn    & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      lstm-crf-lstm   & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      hmm-1+F         & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      hmm-2+F         & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      hmm-3+F         & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      hmm-3+F+ST      & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      crf+F           & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      lstm-crf+F      & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      lstm-crf-cnn+F  & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      lstm-crf-lstm+F & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Precision, recall and F1 in the complete dataset}
  \label{tab:experiment1}
\end{table}

A named entity was only considered correct when 
it was an exact match of the corresponding entity in the data file. 
Models were trained on each of the five sets separately and tested
in the same test set, and each model was trained on each of the five 
sets and evaluated on the same validation and test sets.

>>>>

Web data extraction (WDE) is the task of automatically extracting structured information
from unstructured or semi-structured web documents. The input usually consists of
web documents containing a number of predetermined entities organized in a similar 
manner and the information extraction task consists of identifying these entities
and organizing them according to a template. In this context, named entity recognition
(NER) is a subtask that aims to detect named entities in the text and classify them into 
predetermined categories such as person names, locations or organizations.

HTML documents most often lie in between the structured / unstructured data paradigm.
DOM hierarchy, element disposition, class names, and other features related to 
the document structure and indirectly associated with the data itself can be valuable 
information in the task of identifying entities and determining relationships. Yet we 
cannot expect these features to be completely constrained by an underlying pattern. 
Organization patterns tend to follow some guidelines but are in no way subject to 
strict rules. That is why classical information extraction systems such as automatic
wrapper generators usually do not translate well across different websites.

Most existing web data extraction methods are tailored to extract data from a single
web page \cite{Crescenzi2001, Arasu2003, Freitag1998, Califf1999, Soderland1999,
Kushmerick2000, Hsu1998, Muslea1999}, producing different compromises between efficacy
and degree of human supervision. More recent unsupervised approaches proposed to
tackle the problem of data extraction for whole application domains \cite{Zhu2005, Zhu2006, 
Abdessalem2010, Furche2012, Furche2012a}. Unsupervised WDE methods usually operate in at
least two steps: record segmentation and attribute labelling. Record segmentation
is essentially clustering visually and structurally similar web page regions and 
identifying repeating data records. Attribute labelling is the task of identifying
attributes in data records. Doing any of these tasks well can help performing the 
other task, since patterns that are present in some data records can help identifying 
attributes in other data records. And by properly identifying attributes, we are better 
able to determine the boundaries of data records and segment them with increased accuracy.

In recent years, we saw an astonishing progress in Natural Language Processing.
However, despite WDE being a closely related field of research,
many tools rely on heuristics or hand coded rules to perform record segmentation,
and many methods resort to regular expressions or gazetteer matching to perform attribute
labelling. While these approaches can be sufficient to extract information from webpages
with similar templates, and identifying attributes with distinct formats like prices and
dates, we still lack a sufficiently flexible and intelligent approach to handle more complicated cases.
Even when extracting data from web documents only, data records may contain pure text with 
relevant named entities. Also, many WDE algorithms can effectively exploit the semi-
structure of web documents, but when a method relies too much on structural features, it
often produces poor generalization on cross website extraction tasks. Contrastingly, we 
understand that statistical based approaches can be much more flexible.

In this paper, we investigate the attribute labelling task in WDE with a named entity 
recognition framework. Recently proposed neural architectures have achieved exciting results 
on the NER task on plain text \cite{Huang2015, Lample2016, Ma2016} while requiring almost 
no feature engineering or gazetteers. NER on HTML poses a different type of challenge, 
because web pages are often very different from plain text. Named entities may be present 
inside tables, lists, graphs or other types of visual elements that provide
little to no textual information that could give hints about the semantic category of 
a word. However we show that we can get exceptional performance even with this limitation
and small training sets.

By reliably detecting named entities, we can improve the performance of existing WDE 
approaches or even construct a full machine learning based tool to tackle domain wide
extraction with great flexibility. To test different NER approaches from the perspective 
of web data extraction,
we explored the task of person names extraction from university faculty listings.
Researcher affiliation is often missing from many entries in public databases 
and the display of information varies significantly between different university 
websites, so this task can provide a good measure of the expected performance and
data need for other web data extraction tasks.

@@

Most data extraction systems focus on extracting information from single websites
and are therefore unsuited for cross website extraction tasks. Even unsupervised
approaches that are domain independent, such as RoadRunner \cite{Crescenzi2001} 
and EXALG \cite{Arasu2003} only work well for extracting data from pages generated 
from the same template. A statistical approach to unsupervised domain 
independent web data extraction was described by Zhu et al \cite{Zhu2005}. The 2D CRF 
model takes a web page segmented into data blocks and employs a two dimensional conditional 
random field model to perform attribute labelling. The model was further improved in 
\cite{Zhu2006} to model record segmentation and attribute labeling as a joint task.
Some of the limitations of early unsupervised methods 
were also tackled by ObjectRunner (\cite{Abdessalem2010}) and AMBER (\cite{Furche2012}). 
These methods work by annotating webpages automatically with regular expressions, gazetteers and 
knowledge bases. They can rectify low quality annotations and even improve the annotators
by exploring regular structures in the DOM during the record segmentation phase.

Web data extraction methods have undoubtedly improved extraordinarily, but
as pointed by Schulz et al. \cite{Schulz2016}, it is difficult to compare the results 
achieved by competing tools, and many seem to rely excessively on certain heuristics.
In that regard, the impressive advancements in NLP may provide for more robust and
flexible extraction tools.

@@

Most web data extraction systems rely on hand crafted rules or gazetteers to perform
attribute annotation. Machine learning approaches to NER can improve annotations of 
more complex entities and even manage entity detection without resorting to a gazetteer.
We explored multiple approaches to the Named Entity Recognition problem in the context 
of a web information extraction task. We first introduce two traditional approaches, 
namely: Hidden Markov Models and Linear Chain Conditional Random Fields. And further
we explore neural architectures.

@@

\begin{itemize}
\item Train the HMM with the training set without HTML features.
\item Compute labels for the new websites with the trained HMM.
\item Use these computed labels as a proxy for the actual labels in the 
new websites and estimate HTML feature frequencies only in the new websites.
\item Recompute the labels using the HTML features.
\end{itemize}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{pics/rnn_network}
  \caption{RNN for NER}
  \label{fig:rnn_network}
\end{figure}

Recurrent neural networks (RNN) have been succesfully employed on numerous NLP tasks such as
language modelling, POS tagging, speech recognition and NER. Different from feedforward neural networks, 
RNNs can retain information in their internal state, making them more suitable for processing sequences, 
and consequently for solving text related tasks. In NER, the network outputs one label for each input 
vector as showed in Figure \ref{fig:rnn_network}.

@@

\begin{flalign*}
\Gamma_i^{<t>} &= \sigma(W_i[x^{<t>},h^{<t-1>}] + b_i) &\\
\Gamma_f^{<t>} &= \sigma(W_f[x^{<t>},h^{<t-1>}] + b_f) &\\ 
c^{<t>}        &= \Gamma_f^{<t>} \circ c^{<t-1>} + \Gamma_i^{<t>} tanh(W_c[x^{<t>},h^{<t-1>}] + b_c) &\\
\Gamma_o^{<t>} &= \sigma(W_o[x^{<t>},h^{<t-1>}] + b_o) &\\
h^{<t>}        &= \Gamma_o^{<t>} \circ tanh(c^{t}) &
\end{flalign*}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{pics/lstm_cell}
  \caption{LSTM Cell}
  \label{fig:lstm_cell}
\end{figure}

where $ \sigma $ is the logistic sigmoid function. $ \Gamma_i $, $ \Gamma_f $, and $ \Gamma_o $ are the input,
forget and output gates, respectively. And $ W $ with a subscript is the weight 
matrix corresponding to that gate. Variable $ c^{<t>} $ is the cell 
state and $ h^{<t>} $ is the hidden state, with the vector $ [x^{<t>},h^{<t-1>}] $ 
being formed by concatenating the current input vector $ x^{<t>} $ and the hidden vector 
from the previous timestep $ h^{<t-1>} $. A visual description of our LSTM cell is 
provided in figure \ref{fig:lstm_cell}.
This implementation differs from the LSTM cell described in Huang et al. \cite{Huang2015}
in that the input gate $ \Gamma_i $ and the forget gate $ \Gamma_f $
do not take input from the previous cell state $ c^{<t-1>} $ and the output gate does
not take input from the current cell state $ c^{<t>} $. The cell state and the control gates 
are what makes the LSTM cell better at modelling long term dependencies in comparison
to a regular RNN.

@@

\subsubsection{LSTM-CRF}
\label{sssec:lstm_crf}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{pics/bi_lstm_crf}
  \caption{Bidirectional LSTM-CRF}
  \label{fig:bi_lstm_crf}
\end{figure}

Huang et al. \cite{Huang2015} proposed a bidirectional LSTM with a CRF layer (LSTM-CRF) on the output to tackle
the sequence tagging problem. The CRF layer jointly decodes labels for the whole sentence instead
of predicting each label individually. This architecture achieved an F1 score of 90.10 on the English
data from CONLL-2003 shared task \cite{Sang2003}, in contrast to 85.17 for a bidirectional LSTM without the CRF layer. 
In our experiments, the LSTM-CRF architecture used a bidirectional LSTM with 100 
hidden states, no peepholes and an input and output dropout layers with a dropout
rate of 0.5. The dropout layers have proven to be very important to prevent overfitting 
and allow better generalization.

\subsubsection{LSTM-CRF + CNN character representations}
\ref{sssec:lstm_crf_cnn}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{pics/cnn}
  \caption{CNN}
  \label{fig:cnn}
\end{figure}

Ma and Hovy \cite{Ma2016} proposed adding a convolutional neural network (CNN) layer 
on top of a bidirectional LSTM-CRF to encode character-level information. The CNN
layer is described visually in Figure \ref{fig:cnn}, it receives
only character embeddings as inputs. The character representations generated by the CNN 
are combined with word level representations and then fed to the Bidirectional LSTM with
a CRF output layer described in section \ref{sssec:lstm_crf}.
This architecture can learn morphological features that are very
useful in the NER task, since similar named entities often present morphological similarities. 
This architecture obtained an F1 score of 91.21 in the ConLL2003 dataset. In our experiments, 
the LSTM-CRF architecture with CNN character representations uses a one dimensional convolutional 
neural network with 30 filters and a window size of three characters on top of the LSTM-CRF architecture.
The character embeddings fed to the CNN had 30 dimensions that were randomly initialized.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{pics/lstm_char_representations}
  \caption{LSTM character representations}
  \label{fig:lstm_char}
\end{figure}

Lample et al \cite{Lample2016} suggested using an a bidirectional LSTM to model character-level 
representations on a bidirectional LSTM-CRF. Combining both the forward and backward 
LSTM representations to form the character representation, as described in figure \ref{fig:lstm_char}. 
This character representation is also combined with a word representation and fed to a LSTM-CRF network. 
The forward LSTM is expected to be a better
representation of the suffix of a token, and the backward LSTM is expected to be a
better representation of the prefix of a token. This differentiates the architecture
from the CNN based approach described in Section \ref{sssec:lstm_crf_cnn}, because CNN filters 
discover positional invariant features, while LSTMs can better represent suffixes and prefixes. In our experiments, 
the LSTM-CRF architecture with LSTM character representations was implemented with a bidirectional LSTM
with 25 hidden states, producing character representations of size 50. The character embeddings
had 30 dimensions that were randomly initialized.

@@

The neural models were trained with mini batch Stochastic Gradient Descent over 50 epochs with batch size 10,
learning rate 0.01, momentum 0.9 and decay rate 0.05. We used early stopping \cite{Caruana2000} to select the best 
parameters, considering the F1 measure in the validation set. All neural models used 
GloVe 100-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training,
they have a vocabulary size of 400.000 words.
In the case of NER on HTML, word embeddings work similar to a gazetteer. Named entities 
of a same type have similar embeddings, so good word embeddings can achieve exceptional 
performance with little training and without a gazetteer.

@@

We constructed a novel dataset to evaluate the performance of multiple NER models
at the web information extraction task. The task consists of finding researcher
names in faculty listings from multiple web pages. This would be the 
first step in linking researcher profiles from university websites to their entries
in public databases such as DBLP \footnote{http://dblp.uni-trier.de/}. Unlike many
information extraction datasets, each web page in the dataset comes from a different 
website, and therefore has a different format, what makes many information
extraction approaches impractical. The idea is to explore systems that are general 
enough to allow efficient name extraction from many different sources while requiring
no supervision between different websites.

This task would be similar to the task of labeling authors in comments
However, we wanted to evaluate models without relying on any sophisticated data record
segmentation system. In many cases, entity annotation may precede the segmentation
phase in web data extraction methods, so annotators have to be able to work with
raw HTML data. Because of the type of documents present in the dataset, many sentences 
contained only one or two tokens, while other documents contained long texts.
Finally, all tokens were tagged using the IOB scheme put forward by
Ramshaw and Marcus \cite{Ramshaw1995}.

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l| }
      \hline
      Feature & Description \\
      \hline
      1  & Unaccented lowercase token \\
      2  & Exact gazetteer match \\
      3  & Partial gazetteer match \\
      4  & Log name gazetteer count\\
      5  & Log word gazetteer count\\
      6  & Email \\
      7  & Number \\
      8  & Honorific \\
      9  & URL \\
      10 & Is capitalized \\
      11 & Is a punctuation sign \\
      12 & HTML tag + parent \\
      13 & CSS class \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Features present in the bla dataset}
  \label{tab:features}
\end{table}

The unaccented lowercase token was used as the key for the Glove-100 embedding lookup.
A gazetteer was constructed from a researcher list extracted from DBLP with 1.595.771
names. Feature 2 represents an exact match of a sequence of tokens to any of the 1.595.771 
names, and feature 3 represents a partial match. Feature 4 is the rounded logarithm of 
the frequency of a token in the gazetteer, and feature 5 is the rounded logarithm of the frequency
of a token in a word corpus obtained through a random crawl in university websites.
Features 6 to 11 represent a simple regular expression match to an email, number, 
honorific, URL, capitalization and punctuation sign.

Feature 12 represents the HTML enclosing tag and its parent concatenated. Feature 13
represents all CSS classes concatenated. These features are not very useful in a general
sense, because every HTML document has a different format, so only because a named entity
occurs inside a given HTML tag in a document we cannot say it is more likely to be the case 
in other documents. However, these features can be trained with the self-training strategy 
for HMMs described in section \ref{sssec:self_training}. In all other models these features 
were ignored.

@@

We conducted two experiments to evaluate the best models for named entity recognition
on HTML in the context of web data extraction. In the first experiment, we used the
whole training set (90 documents). In the second experiment, the training set was split 
into five non overlapping sets with only 18 documents, but the test set was kept unchanged. 
The goal of this second experiment 
was to evaluate models when training data is scarce, since labelling data can be a very 
time consuming task.

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l|l|l|l|l|l| }
      \hline
      \multirow{2}{*}{Model} & \multicolumn{3}{c|}{Validation} & \multicolumn{3}{c|}{Test} \\
                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1}
                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1} \\
      \hline
      hmm-1	      & 0.6965 & 0.5749 & 0.6299 & 0.6263 & 0.4431 & 0.5190 \\
      hmm-2	      & 0.7047 & 0.6286 & 0.6645 & 0.6480 & 0.5222 & 0.5783 \\
      hmm-3	      & 0.6127 & 0.6141 & 0.6134 & 0.5471 & 0.4634 & 0.5018 \\
      crf	      & 0.7237 & 0.6650 & 0.6931 & 0.6734 & 0.5879 & 0.6278 \\
      lstm-crf        & 0.8607 & 0.8848 & 0.8726 & 0.8546 & 0.8294 & 0.8418 \\
      lstm-crf-cnn    & 0.9221 & 0.9206 & 0.9214 & 0.9030 & 0.8283 & 0.8640 \\
      lstm-crf-lstm   & 0.9129 & 0.9441 & 0.9282 & 0.8906 & 0.8807 & 0.8856 \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Precision, recall and F1 in the complete dataset}
  \label{tab:experiment1}
\end{table}

Experiment 1 consists of testing the models on the complete NER on HTML dataset 
described in section \ref{sec:ner_dataset}. Table \ref{tab:experiment1} shows the 
results for models that employed no features, except for the words in the text
in the case of HMMs and Glove-100 word embeddings in the case of CRFs and Neural Models.
Without carefully designed features and a gazetteer, HMMs and CRFs have a very 
poor performance, achieving only 57.83 for HMM-2 and 62.78 for CRF in the test set. 
The neural models however achieved high F-scores, even with no features. The
plain LSTM-CRF architecture improved significantly in comparison to the conventional CRF,
and the LSTM-CRF architectures with neural character representations boosted the F1 score
by 2.32 for CNN representations and 4.38 for LSTM representations, showing that they are 
able to learn morphological features automatically, and that at least in the NER tasks LSTM 
character representations are superior, perhaps because they are able to differentiate 
suffixes and prefixes, while CNNs are position invariant. This experiment also shows that
pretrained word embeddings can be used to identify named entities in HTML, where
textual context is very limited without resorting to gazetteers.
